Viscous Erosion in Porous Media

### 2018-04-03 docs/methods/erosion_methods.tex
NM

Briefly, to validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}. In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$. To assess error, we measure the aggregate $L_2$ difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution. Note that this metric is sensitive to numerical errors in any of the simulated bodies. The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver. The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution. Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.

>>>>

Briefly, to validate the multi-body simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}. In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$. To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution. Note that this metric is sensitive to numerical errors in any of the simulated bodies. The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multi-body interactions are handled correctly by the Stokes solver. The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution. Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.
